---
title: "Peer Assignment 1 - Reproducible Research"
date: "Sunday, August 17, 2014"
output: html_document
---
Loading and preprocessing the data

```{r}

  d <-"C://Users//bellechr//Downloads//RStudio//_OnWork//PeerAssestment1"
  setwd(d)
  print (paste("Working Directory =",getwd()))
  
  cFileName<-"activity.csv"
  x <- read.csv(cFileName)
  View(x)

```
What is mean total number of steps taken  per day?
1.  Make a histogram of the total number of steps taken each day
```{r, echo=FALSE}
  totStepsPerDays <- tapply(x$steps, x$date, sum)
  avgSteps <- tapply(x$steps, x$date, mean)
  medSteps <- tapply(x$steps, x$date, median)
  barplot(totStepsPerDays)

```
2. calculate and report the mean and median total number of steps taken per day
```{r, echo=FALSE}
  avgSteps
  medSteps
```
What is the average daily activity pattern?

1. Make a time series plot(i.e type="l") of the  5-minute interval (x-axis) and the average number
of steps taken, averaged across all day (y-axis)

2. Which 5-minute interval, on avetage across all the days in the dataset, contains the maximum number of steps?
```{r, echo=FALSE}

  rx <- as.Date("2012-10-01")
  y0 <- data.frame((as.Date(x$date)- as.Date(rx))+1, x)
  names(y0) <-c("index", "steps", "date", "interval")  
  y <- data.frame(y0, y0$index*y0$interval)
  names(y) <-c("index", "steps", "date", "interval","timeseries")

  mx <- max(y$steps, na.rm=TRUE)
  mx

  rowMaxNo <-subset(y,y$steps==mx)
  rowMaxNo


```
Imputing missing values
toDo

Are there differences in activity patterns between weekdays and weekends?
1. Create a new factor variable in the dataset with two levels -"weekday" and "weekend" indicating 
whether a given date is a weekday or weekend day

2. Make a panel plot containing a time series plot of the 5-minutes interval (x-axis) and 
the average number of steps taken, averaged across all weekday days or weekend days (y-axis).


```{r, echo=FALSE}
  weekend <- c("Saturday","Sunday")
  z <- data.frame(y, weekdays(as.Date(y$date),abbreviate=FALSE),weekdays(as.Date(y$date),abbreviate=FALSE) %in% weekend)
  names(z) <-c("index", "steps", "date", "interval", "timeseries","dayName","isWeekend")  
  
  zWeekend <- subset(z,z$isWeekend==TRUE)
  zWeekday <- subset(z,z$isWeekend==FALSE)
  totStepsPerWeekend <- tapply(zWeekend$steps, zWeekend$date, sum)
  totStepsPerWeekday <- tapply(zWeekday$steps, zWeekday$date, sum)
  plot(totStepsPerWeekend, type="o")
  plot(totStepsPerWeekday,type="o")


```



